\vspace{-1em}Guidance, Please! Towards a Framework for RDF-based Constraint Languages.

### 2015-07-24 paper/paper 2/dc-2015.tex
feedback Kai

The properties describing a simple constraint are very structural\tb{Kai, do you mean structured?}. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be the SPARQL function REGEX where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

@@

In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.\tb{Aus der generischen Repräsentierung können die SPIN mappings zur Validierung generiert werden? das verstehe ich nicht} The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper. The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 constraint types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
The full definition of all constraint types and the generic representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.

@@

We think that this approach is suitable
\begin{enumerate}
  \item to implement the validation of constraints consistently across constraint languages,
  \item to support the extension of constraint languages by means of a simple mapping\tb{was genau meinst du damit? wenn weitere constraint typen unterstützt werden sollen?}, and
  \item to enhance or rather establish the interoperability of different constraint languages.
\end{enumerate}

>>>>

The properties describing a simple constraint are very structural, i.e., the properties describe the structure of constraints. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be the SPARQL function REGEX where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

@@

In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which can directly be validated by providing a mapping from the generic representation to SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language. The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper. The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 constraint types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
The full definition of all constraint types and the generic representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.

@@

We think that this approach is suitable
\begin{enumerate}
  \item to implement the validation of constraints consistently across constraint languages,
  \item to support the extension of constraint languages when additional constraint types should be supported by means of a simple mapping, and
  \item to enhance or rather establish the interoperability of different constraint languages.
\end{enumerate}
